\begin{problem}
  Prove that no index set is immune.

  % \begin{definition}
  %   A set $S$ is an \emph{index set} if it contains the codes of
  %   partial computable functions.
  % \end{definition}

  \begin{answer}
    A set $S$ is \emph{immune} if it is infinite but has no
    infinite c.e. subset.

    Let $I$ be an index set.
    
    \begin{enumarabic}
      \item If $I$ is finite, then $I$ is trivially not immune.
        In fact, the padding lemma tells us that for any
        $e$, there are infinitely many indices $f$ such that
        $\varphi_e = \varphi_f$, and $I$ must contain
        any such $f$ for any $e$ that it contains.
        Therefore, if $I$ is finite, then $I = \emptyset$.
      \item Now, suppose $I$ is infinite.
        Let $\varphi_\ell$ be a turing machine that simulates
        $\chi_I$. Since $I$ is not necessarily computable,
        $\varphi_\ell$ does not necessarily halt on some inputs
        --- but since $I$ is infinite, we know that
        $\varphi_\ell$ \emph{eventually} halts (and returns $1$)
        on infinitely many inputs.

        Then we can construct an infinite c.e. subset $S \subseteq I$
        as follows.

        \step
        Define
            \begin{align*}
              f : \omega^2 &\to \set{0, 1} \\
              f(e, k) &= \begin{cases}
                1 & \text{if $\varphi_{\ell,k}(e) \convergesto 1$} \\
                0 & \text{otherwise.}
              \end{cases}  
            \end{align*}
        
        For $n = 0, 1, 2, 3, \ldots$,
        Define \[ I_n = \set{e \mid f(e, n) = 1}. \]

        \step
        First, we claim that each $I_n$ is c.e.
        --- in fact, it is computable.
        Given an input $e$, we only need to simulate
        $\varphi_{\ell}(e)$ for $n$ steps to determine
        if $e \in I_n$ or not.

        \step
        Next, We claim that there exists an $n$ such that
        $I_n$ is infinite.
        For the sake of contradiction, suppose $I_n$ is finite for all $n$.
        This implies that for any given $n$ (no matter how arbitrarily
        large), there are only finitely many $e$ such that
        $\varphi_{\ell,n}(e) \convergesto 1$, which implies that
        $\varphi_{\ell}$ converges for only finitely many $e$,
        hence $I$ itself is finite.
        This contradicts the condition that $I$ is infinite.

        \step
        Thus, for any index set $I$, there exists some $n$ such that
        $I_n$ as constructed above is an infinite, c.e. subset
        of $I$ --- hence $I$ is not immune.
    \end{enumarabic}
  \end{answer}
\end{problem}
