\begin{problem}
  Use a diagonalization argument to show that there is no
  uniform listing of all characteristic functions
  of the computable sets.

  \begin{answer}
    Suppose, for the sake of contradiction, that there is a uniform listing of all characteristic functions of the computable sets.
    Let $\varphi_e$ be the $e$-th characteristic function in this listing.
    We will construct a new characteristic function $\varphi$ that is not in this listing.

    Define $\varphi$ as follows:
    \[
      \varphi(n) = \begin{cases}
        1 & \text{if } \varphi_n(n) = 0 \\
        0 & \text{otherwise}
      \end{cases}
    \]

    We claim that $\varphi$ is a characteristic function of a computable set.
    \begin{itemize}
      \item $\varphi$ is total computable because it is defined by a finite number of operations.
      \item $\varphi$ is characteristic because it is defined in terms of the characteristic function $\varphi_n$.
    \end{itemize}

    We will show that $\varphi$ is not in the listing.
    Suppose, for the sake of contradiction, that $\varphi = \varphi_e$ for some $e$.
    By definition of $\varphi$, we have:
    \begin{align*}
      \varphi(e) = 1 &\iff \varphi_e(e) = 0 \\
      \varphi(e) = 0 &\iff \varphi_e(e) = 1
    \end{align*}
    This means that $\varphi$ and $\varphi_e$ disagree at $e$.
    Therefore, $\varphi \neq \varphi_e$, contradicting the assumption that $\varphi = \varphi_e$.
    Therefore, $\varphi$ is not in the listing, meaning
    there is no uniform listing of all characteristic functions of the computable sets
    since we can always, find a characteristic function not included in the listing.
  \end{answer}
\end{problem}
