\begin{problem}
  Which two times are most convenient as office hours?
  \begin{answer}
    \begin{enumarabic}
      \item Monday 3:30-4:30pm
      \item Wednesday 3:30-4:30pm
    \end{enumarabic}
  \end{answer}
\end{problem}


\begin{problem}
  Give one hour which would be your most ideal time to visit office hours.
  \begin{answer}
    Any time Wednesday afternoon (after class) works best for me,
    including 3:30-4:30pm.
  \end{answer}
\end{problem}

\begin{problem}
  How familiar are you with proof-based math?
  \begin{answer}
    I am very familiar with proof-based math, having done
    a lot of it in some of my previous courses.
    \begin{enumarabic}
      \item MATH 22 (Linear Algebra)
      \item MATH 63 (Real Analysis)
      \item MATH 69 (Logic)
      \item MATH 71 (Algebra)
      \item MATH 75 (Cryptography)
      \item MATH 100 (Game Theory)
      \item COSC 30 (Discrete Mathematics)
      \item COSC 31 (Algorithms)
      \item COSC 39 (Theory of Computation)
      \item COSC 83 (Computer Vision) --- linear algebra proofs
    \end{enumarabic}
  \end{answer}
\end{problem}

\newpage
\begin{problem}
  How comfortable are you with proof-based math?
  \begin{answer}
    I feel comfortable with proof-based math.
    The only caveat I feel is that it always takes me a while
    to learn how to efficiently articulate proofs in a new context
    especially if there is a lot of notation involved.
  \end{answer}
\end{problem}

\begin{problem}
  Are there any specific proof techniques or writing strategies
  you’d like to improve on throughout the course?
  \begin{answer}
    I am not sure yet about specific proof techniques,
    but I am most excited to learn new ideas,
    especially having some context around
    computability (coming from \newterm{decidability} in Logic
    and \newterm{NP completeness} in Algorithms \& Automata Theory).

    \step
    I am particularly interested in
    \href{https://plato.stanford.edu/entries/lambda-calculus/}{\newterm{$\lambda$-calculus}}
    and functional programming
    (I have some experience with \href{https://www.haskell.org/}{Haskell}) ---
    I am thinking of them as potential directions for the final project
    if I can find a connection with computability.
  \end{answer}
\end{problem}
